Trifunctional Phosphatidylinositol 3,4,5-*tris*phosphate

### 2025-03-07 Background/DataAnalysisAndStatistics.qmd
editing from Frank's suggestions, removing CNET

To ensure consistency across all publicly available mass spectrometry datasets that used TMT isobaric mass tagging, we applied the same standardized analysis pipeline previously published. This approach allows for better comparability between datasets. Several of the datasets included in this repository were generated and analyzed at the European Molecular Biosciences Laboratories (EMBL) in Heidelberg, Germany, where Dr. Frank Stein developed and implemented the data analysis pipeline.
In summary, we processed the mass spectrometry (MS) data using FragPipe[@yuAnalysisDIAProteomics2023], following established methodologies outlined in Farley et al. (2024, A), Farley et al. (2024, B), and Thomas et al. (2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025]. To ensure accurate protein identification, we used a UniProt FASTA database that included common contaminants and reversed sequences for validation. Proteins were included in the final dataset only if they contained at least two unique peptides, each at least seven amino acids long.

To account for potential technical variations across experiments, we applied a normalization step using the 'removeBatchEffect' function from the limma package, stabilizing variance in log2-transformed TMT reporter ion intensities[@huberVarianceStabilizationApplied2002; @ritchieLimmaPowersDifferential2015]. Further normalization was carried out using the 'normalizeVSN' function of the same package. We identified differentially expressed proteins using the moderated t-test within limma, incorporating replicate information into the statistical model through the 'lmFit' function.

@@

#### Gene Ontology Dot Plots

#### Gene Ontology CNET maps

>>>>

To ensure consistency across all publicly available mass spectrometry datasets that used TMT isobaric mass tagging, we applied the same standardized analysis pipeline previously published in Farley et al. (2024, A), Farley et al. (2024, B), and Thomas et al. (2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025]. This approach allows for better comparability between datasets. Several of the datasets included in this repository were generated and analyzed at the European Molecular Biosciences Laboratories (EMBL) in Heidelberg, Germany, where Dr. Frank Stein developed and implemented the data analysis pipeline.

In summary, we processed the mass spectrometry (MS) data using FragPipe[@yuAnalysisDIAProteomics2023]. The protein search was performed using a UniProt FASTA database with one entry per gene, excluding isoforms and minimizing TrEMBL entries. Common contaminants and reversed sequences were also included for validation. Proteins were included in the final dataset if they contained at least two razor peptides, as FragPipe applies the Occam’s Razor principle, assigning shared peptides to the protein with the highest supporting evidence.

For the database search, we included post-translational modifications (PTMs) such as oxidation (M), acetylation (N-term), and carbamidomethylation (C). The raw files were analyzed using FragPipe's protein.tsv output, which was used as the basis for downstream quantification.

To account for potential technical variations across experiments, we applied a normalization step using the 'removeBatchEffect' function from the limma package to correct for batch effects in log2-transformed TMT reporter ion intensities[@huberVarianceStabilizationApplied2002; @ritchieLimmaPowersDifferential2015]. Further normalization was carried out using the 'normalizeVSN' function of the same package. We identified differentially expressed proteins using the moderated t-test within limma, incorporating replicate information into the statistical model through the 'lmFit' function.

@@

### 2025-03-07 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET

---
title: "Trifunctional Phosphatidylinositol 3,4,5-*bis*phosphate"
subtitle: "PI(3,4,5)P~3~"
---

@@

>>>>

---
title: "Trifunctional Phosphatidylinositol 3,4,5-*tris*phosphate"
subtitle: "PI(3,4,5)P~3~"
prefer-html: true
---

@@

:::{.border}
![Trifunctional Phosphatidylinositol 3,4,5-*tris*phosphate. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
:::
